\cvsection{Experience}

\begin{cventries}
  \cventry
    {Software Engineer} % Job title
    {Box} % Organization
    {Redwood City, CA} % Location
    {August 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Co-leading the migration and rearchitecture of Box API data collection and report generation of 3.8 to 114 billion rows of data daily from cron jobs to Apache Spark jobs. This decreases compute time per cluster and increases fault tolerance.}
        \item{Developed and maintained the open source Box SDKs in Github to allow people to integrate with Box's API. Over 1.3 million API calls are made ever minute through the SDKs.}
        \item{Worked with the Java, .NET, Python, Node.js, iOS content, iOS preview SDKs and a CLI.}
        \item{Worked on networking in the iOS content SDK by rewriting the network layer to reduce the SDK size by 70\%, reducing writes to disk and adding support for video streaming.}
        \item{Helped lead the intern interview hiring process and implemented tooling to make the take home project more convenient and inclusive for students.}
        {\setlength \itemindent{-2ex} \itemsep2pt \item[] \textbf{Technologies:} Java, .NET, Python, Node.js, Swift}
        {\setlength \itemindent{-2ex} \itemsep2pt \item[] 
        \href{https://sujaygarlanka.com/experience.html\#box}{ \faInfoCircle \textbf{\color{awesome}{ Details}}}
        \href{https://github.com/box/sdks}{ \faGithub \textbf{\color{awesome}{ Code}}}}
      \end{cvitems}
    }
    
  \cventry
    {Software Engineer Intern} % Job title
    {Box} % Organization
    {Redwood City, CA} % Location
    {May 2018 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Built an open source command line tool for accessing 200 of Box’s API endpoints}
        \item{Incorporated JWT authentication with Box in the CLI}
        \item{Included features such as interactive CLI with prompting, bulk input and bulk output}
        \item{Released publicly and handles around 10k requests per minute}
        {\setlength \itemindent{-2ex} \itemsep2pt \item[] \textbf{Technologies:} Node.js, Oclif CLI Framework, Mocha Testing Framework}
        {\setlength \itemindent{-2ex} \itemsep2pt \item[]  \href{https://sujaygarlanka.com/experience.html\#internship}{ \faPlayCircle \textbf{ Demo}} \href{https://github.com/box/boxcli}{ \faGithub \textbf{ Code}}}
      \end{cvitems}
    }

  \cventry
    {Software Engineer Intern} % Job title
    {Cisco} % Organization
    {Morrisville, NC} % Location
    {May 2017 - July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Created a proof of concept (POC) for an internal tool to digitize the creation and management life cycle of existing legal documents}
        \item{Designed and implemented the tool to select the correct form based on user responses, insert the form inputs into a PDF of the appropriate legal document, and track it through the approval and review process}
        \item{Integrated it with the DocuSign API for e-signatures and approval}
        {\setlength \itemindent{-2ex} \itemsep2pt \item[] \textbf{Technologies:} AngularJS, Node.js, MongoDB, Express.js}
      \end{cvitems}
    }
    
    \cventry
    {ECE Teaching Assistant} % Job title
    {Duke} % Organization
    {Durham, NC} % Location
    {August 2017 - December 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Teaching assistant for microelectronics devices and circuits class for Dr. Aaron Franklin}
        \item{Held office hours, review sessions and graded homework}
        \item{Awarded TA of the semester}
      \end{cvitems}
    }
\end{cventries}
